---
title: "SCA1 - Assignment 2"
author: "Thanh Tran Viet-h12430817, Krishna Varun Varma Kalidindi-h12438206, Iryna Ustych-h12427988"
date: "16 October 2024"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1

## Question a

Sets:\
I: the set of product types, $I = \{1, 2, 3\}$\
J: the set of manufacturing departments, $J = \{A, B, C\}$

Indices:\
i: product type, $i \in I$\
j: manufacturing department, $j \in J$

Parameters:\
$p_i$: the profit contribution per unit of product type i\
$C_j$: the labour hour capacity of manufacturing department j\
$c_{ij}$: the labour hour used for producing a unit of product type i at manufacturing department j

Decision variables:\
$x_i$: the quantity of each product type i to be produced

Objective function:\
Maximizing total profit contribution
$$Max \sum_{i \in I} p_ix_i$$

Constraints:\
For each manufacturing department j, the total labour hour used must not exceed the labour hour capacity: $$\sum_{i \in I} c_{ij}x_i \leq C_j, \forall j \in J$$\
For each product type i, the produced quantity must be non-negative: $$x_i \geq 0, \forall i \in I$$

## Question b

```{r}
# Clear enviroment
rm(list = ls())

# Import library
library("lpSolve")

# Decision varible coefficients
c1 <- c(22, 25, 28)

# Constraint matrix
A1 <- matrix(c(1.5, 3, 2,
              2, 1, 2.5,
              0.25, 0.25, 0.25),
            nrow = 3,
            ncol = 3,
            byrow = TRUE)

# Constraint direction
dir1 <- c(rep("<=",3))

# Constraint RHS
b1 <- c(425, 375, 55)

# Model
model1 <- lp(direction = "max", 
            objective.in = c1, 
            const.mat = A1, 
            const.dir = dir1, 
            const.rhs = b1, 
            all.int = TRUE)

# Print result
for (i1 in 1:length(model1$solution)) {
  print(paste("The quantity of product type", 
              i1, 
              "that should be produced is", 
              model1$solution[i1]))
}

print(paste("The projected total profit contribution is", 
            model1$objval))
```

## Question c

$s_i$: the setup cost of product type i

When the setup costs associate, the total profit contribution decreases

```{r}
# Setup cost
setup_cost1 <- c(400, 525, 550)

actual_setup_cost1 <- c()

for (i1 in 1:length(model1$solution)) {
  if (model1$solution[i1] >= 0) {actual_setup_cost1[i1] <- setup_cost1[i1]} 
  else {actual_setup_cost1[i1] <- 0}
}

# Calculate revised total profit
revised_total_profit1 <- model1$objval - sum(actual_setup_cost1)

# Print result
print(paste("The total profit contribution after taking into account the setup costs is", 
            revised_total_profit1))
```

## Question d

Sets:\
I: the set of product types, $I = \{1, 2, 3\}$\
J: the set of manufacturing departments, $J = \{A, B, C\}$

Indices:\
i: product type, $i \in I$\
j: manufacturing department, $j \in J$

Parameters:\
$p_i$: the profit contribution per unit of product type i\
$C_j$: the labour hour capacity of manufacturing department j\
$c_{ij}$: the labour hour used for producing a unit of product type i at manufacturing department j\
$s_i$: the setup cost of product type i\
$w_i$: the maximum production quantity of product type i if it is decided to produce

Decision variables:\
$x_i$: the quantity of each product type i to be produced
$y_i$: the decision of producing product type i or not, $y_i \in \{0,1\}$

Objective function:\
Maximizing total profit contribution
$$Max \sum_{i \in I} p_ix_i - \sum_{i \in I} s_iy_i $$

Constraints:\
For each manufacturing department j, the total labour hour used must not exceed the labour hour capacity: $$\sum_{i \in I} c_{ij}x_i \leq C_j, \forall j \in J$$\
For each product type i, the produced quantity must not exceed the maximum production quantity: $$x_i - W_iy_i \leq 0, \forall i \in I$$\
For each product type i, the produced quantity must be non-negative: $$x_i \geq 0, \forall i \in I$$

## Question e

```{r}
# Decision variable coefficient
c2 <- c(22, 25, 28, -400, -525, -550)

# Constraint matrix
A2 <- matrix(c(1.5, 3, 2, rep(0,3),
              2, 1, 2.5, rep(0,3),
              0.25, 0.25, 0.25, rep(0,3),
              1,0,0,-185,0,0,
              0,1,0,0,-125,0,
              0,0,1,0,0,-140),
              nrow = 6,
              ncol = 6,
              byrow = TRUE)

# Constraint direction       
dir2 <- c(rep("<=",6))

# Constraint RHS
b2 <- c(425, 375, 55, rep(0,3))

# Model
model2 <- lp(direction = "max", 
            objective.in = c2, 
            const.mat = A2, 
            const.dir = dir2, 
            const.rhs = b2, 
            int = 1:3,
            bin = 4:6)

# Print result
for (i2 in 1:length(model2$solution[1:3])) {
  print(paste("The quantity of product type", 
              i2, 
              "that should be produced is", 
              model2$solution[i2]))
}

print(paste("The projected total profit contribution is", model2$objval))

print(paste("Comparing the new total profit of", 
            model2$objval,
            "versus the previous one of", 
            revised_total_profit1,
            ", it is higher by", 
            model2$objval-revised_total_profit1))
```

This gap can be explained as in question c solution, product type 3 was only produced by 1 unit which earned 28 profit but costed 550 of fixed setup cost, as a result, total earning for producing product type 3 was -522. Therefore, in the new solution, to ignore that loss, only product type 1 and 2 was produced.

# Problem 2

## Question a

```{r}
# Clear enviroment
rm(list = ls())

# Import library
library(igraph)
library(lpSolve)
library(slam)

# Plants to warehouses cost
plant1_cost1 <- data.frame(i = rep(1,2), j = c(4,5), cost = c(4,7))
plant2_cost1 <- data.frame(i = rep(2,2), j = c(4,5), cost = c(8,5))
plant3_cost1 <- data.frame(i = rep(3,2), j = c(4,5), cost = c(5,6))

# Warehouses to customers cost
wh1_cost1 <- data.frame(i = rep(4,4), j = c(6,7,8,9), cost = c(6,4,8,4))
wh2_cost1 <- data.frame(i = rep(5,4), j = c(6,7,8,9), cost = c(3,6,7,7))

# Edges list
edge_list1 <- rbind(plant1_cost1, plant2_cost1, plant3_cost1, wh1_cost1, wh2_cost1)
edge_list1 <- cbind(edge = 1:nrow(edge_list1), edge_list1)

# Create graph
g1 <- graph_from_data_frame(d = edge_list1[, c("i", "j", "cost")], directed = TRUE)

# Adjust display margin
par(mar = c(1, 1, 1, 1))

# Plot the graph
plot(g1,
     layout = layout_as_tree(g1),
     vertex.color=c("Yellow"),
     vertex.size = 30,
     vertex.label.font=2,
     vertex.label.color = 'black',
     vertex.label.cex=1.1,
     edge.color="gray40",
     edge.width= E(g1)$cost/100,
     edge.label = E(g1)$cost,
     edge.label.cex = 1,
     edge.label.font = 1,
     edge.curved = 0.01,
     edge.arrow.size=.5,
     main = 'Network 1 visualization'
)
```

## Question b

Sets:\
V: Set of all nodes in the network, $V = \{1, 2, ..., 9\}$\
I: Set of origin nodes, $I = \{1, 2, 3\}$\
T: Set of transshipment nodes, $T = \{4, 5\}$\
J: Set of destination nodes, $J = \{6, 7, 8, 9\}$\
A: Set of directed edges between nodes, $(i,k),(k,j) \in A, \forall i,j,k \in V$

Indices:\
i: origin nodes, $i \in I$\
k: transshipment nodes, $k \in T$\
j: destination nodes, $j \in J$\

Parameters:\
$c_{ik}$: the delivery cost per unit from node i to node k\
$c_{kj}$: the delivery cost per unit from node k to node j\
$s_i$: the supply capacity of node i\
$d_j$: the demand of node j

Decision variables:\
$x_{ik}$: the delivery quantity from node i to node k\
$x_{kj}$: the delivery quantity from node k to node j

Objective function:\
Minimizing the total delivery cost
$$Min \sum_{(i, k) \in A} c_{ik}x_{ik} + \sum_{(k, j) \in A} c_{kj}x_{kj}$$

Constraints:\
For each origin node i, the total outbound quantity must not exceed the capacity: $$ \sum_{(i,k) \in A} x_{ik} \leq s_i, \forall i \in I $$
For each destination node j, the total inbound quantity must fulfill the demand: $$ \sum_{(k,j) \in A} x_{kj} \geq d_j, \forall j \in J $$
For each transshipment node k, the inbound and outbound quantity must be equal: $$ \sum_{(i,k) \in A} x_{ik} - \sum_{(k,j) \in A} x_{kj} = 0, \forall k \in T $$
For each edge (i,k) and (k,j), the delivery quantity must be non-negative: $$ x_{ik} \geq 0, x_{kj} \geq 0, \forall (i,k),(k,j) \in A $$

## Question c

```{r}
# delivery cost on each edge
c1 <- edge_list1$cost

# constraints for plants
const1_1 <- data.frame(i = c(1,1), j = c(1,2), v = c(1,1))
const2_1 <- data.frame(i = c(2,2), j = c(3,4), v = c(1,1))
const3_1 <- data.frame(i = c(3,3), j = c(5,6), v = c(1,1))

# constraints for warehouses
const4_1 <- data.frame(i = c(4,4,4,4,4,4,4), j = c(1,3,5,7,8,9,10), v = c(-1,-1,-1,1,1,1,1))
const5_1 <- data.frame(i = c(5,5,5,5,5,5,5), j = c(2,4,6,11,12,13,14), v = c(-1,-1,-1,1,1,1,1))

# constraints for customers
const6_1 <- data.frame(i = c(6,6), j = c(7,11), v = c(rep(1,1)))
const7_1 <- data.frame(i = c(7,7), j = c(8,12), v = c(rep(1,1)))
const8_1 <- data.frame(i = c(8,8), j = c(9,13), v = c(rep(1,1)))
const9_1 <- data.frame(i = c(9,9), j = c(10,14), v = c(rep(1,1)))

var_names1 <- paste0('x', edge_list1$i, edge_list1$j) # Name of edge

# Combine all constraints to a dataframe
const_1 <- rbind(const1_1,const2_1,const3_1,const4_1,const5_1,const6_1,const7_1,const8_1,const9_1)

# Create the sparse matrix of direction value of constraints
const_sparse_1 <- simple_triplet_matrix(i = const_1$i, j = const_1$j, v = const_1$v)
A1 <- as.matrix(const_sparse_1)

colnames(A1) <- var_names1

# Right-hand side setup
b1 <- c(440, 650, 410, 0, 0, 300, 300, 250, 400)

# Constraints direction
dir1 <- c(rep("<=",3),rep("==",2),rep(">=",4))

# Solve
model1 <- lp(direction = "min", 
             objective.in = c1, 
             const.mat = A1, 
             const.dir = dir1, 
             const.rhs = b1, 
             all.int = TRUE)

for (i1 in 1:length(model1$solution)) {
  print(paste("The delivery cost from node", edge_list1$i[i1],
              "to node", edge_list1$j[i1],
              "is", model1$solution[i1]))
}

print(paste("The optimal network cost is", model1$objval))

# Add results column into edgelist to draw graph
edge_list1$shipping1 <- model1$solution
edge_list1$total_cost1 <- edge_list1$cost * edge_list1$shipping1

# Keep only positive edge
edge_list1 <- edge_list1[edge_list1$shipping1 > 0, ]

# Create graph
g1_new <- graph_from_data_frame(d = edge_list1[, c("i", "j")], directed = TRUE)
E(g1_new)$weight <- edge_list1$total_cost1

# Adjust display margin
par(mar = c(1, 1, 1, 1))

plot(g1_new,
     layout = layout_as_tree(g1_new),
     vertex.color=c("Yellow"),
     vertex.size = 30,
     vertex.label.font=2,
     vertex.label.color = 'black',
     vertex.label.cex=1.1,
     edge.color="gray40",
     edge.width= E(g1_new)$weight/1000,
     edge.label = E(g1_new)$weight,
     edge.label.cex = 1,
     edge.label.font = 1,
     edge.curved = 0.01,
     edge.arrow.size=.5,
     main = 'Network 1 result describe - Cost view'
)
```

## Question d

```{r}
# Plants to warehouses cost
plant1_cost2 <- plant1_cost1
plant2_cost2 <- plant2_cost1

# Plant 3 to warehouses and customers cost
plant3_cost2 <- data.frame(i = rep(3,3), j = c(4,5,9), cost = c(5,6,6))

# Warehouses to warehouse and customers cost
wh1_cost2 <- data.frame(i = rep(4,5), j = c(5,6,7,8,9), cost = c(3,6,4,8,4))
wh2_cost2 <- data.frame(i = rep(5,5), j = c(4,6,7,8,9), cost = c(3,3,6,7,7))

# Edges list
edge_list2 <- rbind(plant1_cost2, plant2_cost2, plant3_cost2, wh1_cost2, wh2_cost2)
edge_list2 <- cbind(edge = 1:nrow(edge_list2), edge_list2)

# Create graph
g2 <- graph_from_data_frame(d = edge_list2[, c("i", "j", "cost")], directed = TRUE)

# Adjust display margin
par(mar = c(1, 1, 1, 1))

# Plot the graph
plot(g2,
     layout = layout_as_tree(g2),
     vertex.color=c("Yellow"),
     vertex.size = 30,
     vertex.label.font=2,
     vertex.label.color = 'black',
     vertex.label.cex=1.1,
     edge.color="gray40",
     edge.width= E(g2)$cost/100,
     edge.label = E(g2)$cost,
     edge.label.cex = 1,
     edge.label.font = 1,
     edge.curved = 0.01,
     edge.arrow.size=.5,
     main = 'Network 2 visualization'
)
```

## Question e

Sets:\
V: Set of all nodes in the network, $V = \{1, 2, ..., 9\}$\
I: Set of origin nodes, $I = \{1, 2, 3\}$\
T: Set of transshipment nodes, $T = \{4, 5\}$\
J: Set of destination nodes, $J = \{6, 7, 8, 9\}$\
A: Set of directed edges between nodes, $(i,k),(i,j),(k,k'),(k,j) \in A, \forall i,j,k,k',l \in V$

Indices:\
i: origin nodes, $i \in I$\
k (and k'): transshipment nodes, $k,k' \in T$\
j: destination nodes, $j \in J$\

Parameters:\
$c_{ik}$: the delivery cost per unit from node i to node k\
$c_{ij}$: the delivery cost per unit from node i to node j\
$c_{kk'}$: the delivery cost per unit from node k to node k'\
$c_{kj}$: the delivery cost per unit from node k to node j\
$s_i$: the supply capacity of node i\
$d_j$: the demand of node j

Decision variables:\
$x_{ik}$: the delivery quantity from node i to node k\
$x_{ij}$: the delivery quantity from node i to node j\
$x_{kk'}$: the delivery quantity from node k to node k'\
$x_{kj}$: the delivery quantity from node k to node j

Objective function:\
Minimizing the total delivery cost
$$Min \sum_{(i, k) \in A} c_{ik}x_{ik} + \sum_{(i, j) \in A} c_{ij}x_{ij} + \sum_{(k, k') \in A} c_{kk'}x_{kk'} + \sum_{(k, j) \in A} c_{kj}x_{kj} $$

Constraints:\
For each origin node i, the total outbound quantity must not exceed the capacity: $$ \sum_{(i,k) \in A} x_{ik} + \sum_{(i,j) \in A} x_{ij} \leq s_i, \forall i \in I $$
For each destination node j, the total inbound quantity must fulfill the demand: $$ \sum_{(k,j) \in A} x_{kj} + \sum_{(i,j) \in A} x_{ij} \geq d_j, \forall j \in J $$
For each transshipment node k and k', the inbound and outbound quantity must be equal: $$ \sum_{(i,k) \in A} x_{ik} - \sum_{(k,k') \in A} x_{kk'} - \sum_{(k,j) \in A} x_{kj} = 0, \forall k,k' \in T $$
For each edge (i,k), (i,j), (k,k'), (k,j), the delivery quantity must be non-negative: $$ x_{ik} \geq 0, x_{ij} \geq 0, x_{kk'} \geq 0, x_{kj} \geq 0, \forall (i,k),(i,j),(k,k'),(k,j) \in A $$

## Question f

```{r}
# delivery cost on each edge
c2 <- edge_list2$cost

# constraints for plants
const1_2 <- data.frame(i = c(1,1), j = c(1,2), v = c(1,1))
const2_2 <- data.frame(i = c(2,2), j = c(3,4), v = c(1,1))
const3_2 <- data.frame(i = c(3,3,3), j = c(5,6,7), v = c(1,1,1))

# constraints for warehouses
const4_2 <- data.frame(i = c(rep(4,8)), j = c(1,3,5,8:12), v = c(rep(-1,3), rep(1,5)))
const5_2 <- data.frame(i = c(rep(5,8)), j = c(2,4,6,13:17), v = c(rep(-1,3), rep(1,5)))

# constraints for customers
const6_2 <- data.frame(i = c(rep(6,2)), j = c(9,14), v = c(rep(1,2)))
const7_2 <- data.frame(i = c(rep(7,2)), j = c(10,15), v = c(rep(1,2)))
const8_2 <- data.frame(i = c(rep(8,2)), j = c(11,16), v = c(rep(1,2)))
const9_2 <- data.frame(i = c(rep(9,3)), j = c(7,12,17), v = c(rep(1,3)))

var_names2 <- paste0('x', edge_list2$i, edge_list2$j) # Name of edge

# Combine all constraints to a dataframe
const_2 <- rbind(const1_2, const2_2, const3_2, const4_2, const5_2, const6_2, 
                 const7_2, const8_2, const9_2)

# Create the sparse matrix of direction value of constraints
const_sparse_2 <- simple_triplet_matrix(i = const_2$i, j = const_2$j, v = const_2$v)
A2 <- as.matrix(const_sparse_2)

colnames(A2) <- var_names2

# Right-hand side setup
b2 <- b1

# Constraints direction
dir2 <- dir1

# Solve
model2 <- lp(direction = "min", 
             objective.in = c2, 
             const.mat = A2, 
             const.dir = dir2, 
             const.rhs = b2, 
             all.int = TRUE)

# Print result
for (i2 in 1:length(model2$solution)) {
  print(paste("The delivery cost from node", edge_list2$i[i2],
              "to node", edge_list2$j[i2],
              "is", model2$solution[i2]))
}

print(paste("The optimal network cost is", model2$objval))

# Add results column into edgelist to draw graph
edge_list2$shipping2 <- model2$solution
edge_list2$total_cost2 <- edge_list2$cost * edge_list2$shipping2

# Keep only positive edge
edge_list2 <- edge_list2[edge_list2$shipping2 > 0, ]

# Graph
g2_new <- graph_from_data_frame(d = edge_list2[, c("i", "j")], directed = TRUE)
E(g2_new)$weight <- edge_list2$total_cost2

# Adjust display margin
par(mar = c(1, 1, 1, 1))

# Plot the graph
plot(g2_new,
     layout = layout_as_tree(g2_new),
     vertex.color=c("Yellow"),
     vertex.size = 30,
     vertex.label.font=2,
     vertex.label.color = 'black',
     vertex.label.cex=1.1,
     edge.color="gray40",
     edge.width= E(g2_new)$weight/1000,
     edge.label = E(g2_new)$weight,
     edge.label.cex = 1,
     edge.label.font = 1,
     edge.curved = 0.01,
     edge.arrow.size=.5,
     main = 'Network 2 result describe - Cost view'
)
```

# Problem 3 

## Question a

```{r}
# Clear environment
rm(list = ls())

# Import the data
c1 <- read.csv("D:\\WU\\SCA1\\Exercise 2\\large-scale\\large-scale\\obj_function_coefs_c.csv", 
               row.names = 1) %>% unlist()

# Print the results
print(paste("There are", length(c1), "decision variables" ))
```

## Question b

```{r}
# Import library
library(tidyverse)

# Import the data
A1 <- read.csv("D:\\WU\\SCA1\\Exercise 2\\large-scale\\large-scale\\constraint_matrix_A.csv",
               row.names = 1) %>% as.matrix()

b1 <- read.csv("D:\\WU\\SCA1\\Exercise 2\\large-scale\\large-scale\\constraint_vector_b.csv", 
               row.names = 1) %>% unlist()

# Print the results
print(paste("There are", length(b1), "constraints" ))
```

## Question c

```{r}
# Import library
library(ROI)

# Create names for variable
names <- c()
for (i in 1:length(c1)) {
  names[i] <- paste0("x", i)
}

# Set up the solver
lp  <- OP(objective = L_objective(c1, names=names),
          constraints = L_constraint(L = A1, dir = c(rep("<=",5750)), rhs = b1),
          types = rep("C",length(c1)),
          bounds = V_bound(li = 1:5000, lb = c(rep(0,5000))),
          maximum = TRUE)

# Check the solver
lp

# Time before solve
t1 <- Sys.time()

# Solve the problem with glpk
solution_glpk <- ROI_solve(lp, solver = "glpk")

# Time after solve
t2 <- Sys.time()

# Time different
print(paste("Solving time:", t2 - t1))

# Objective value
print(paste("The optimal objective value is", solution_glpk$objval))
```

## Question d

```{r}
# Print the solution
solution_gplk_df <- data.frame(solution_glpk$solution) %>% 
  rename(solution_value = solution_glpk.solution) %>%
  arrange(desc(solution_value))

head(solution_gplk_df)

# Calculate the share of decision variables that is non-zero
print(paste("The share of non-zero decision variables is", 
            sum(solution_gplk_df$solution_value != 0) / 5000*100,"%"))
```

## Question e

```{r}
# Time before solve
t3 <- Sys.time()

# Solve the with solver
solution_symphony <- ROI_solve(lp, solver = "symphony")

# Time before solve
t4 <- Sys.time()

# Time different
print(paste("Solving time:", t4 - t3))

# Objective value
print(paste("The optimal objective value is", solution_symphony$objval))

# Print the solution
solution_symphony_df <- data.frame(solution_symphony$solution) %>% 
  rename(solution_value = solution_symphony.solution) %>%
  arrange(desc(solution_value))
          
head(solution_symphony_df)

# Calculate the share of decision variables that is non-zero
print(paste("The share of non-zero decision variables is", 
            sum(solution_symphony_df$solution_value != 0) / 5000*100,"%"))

# Compare the 2 results by correlation coefficient
print(paste("Correlation coefficient between 2 solvers' optimal decision variables is:", 
            cor(solution_glpk$solution, solution_symphony$solution)))
  
# Compare the 2 results by visual
plot(solution_glpk$solution, solution_symphony$solution)
```

# Problem 4

## Question a

```{r}
# Clear environment
rm(list = ls())

# Set up sales function
sales_function <- function (x) {
  s = -3*x[1]^2 - 8*x[2]^2 - 6*x[1]*x[2] + 16*x[1] + 34*x[2]
  return(s)
}

# Parameter
x1 <- c(0,1)
x2 <- c(2,1)
x3 <- c(1,0)
x4 <- c(1,2)

# Print results
print(paste("Sales when 0$ is spent on radio ads and $1000 is spent on direct-mail is",
            sales_function(x1)*1000, "$"))
print(paste("Sales when 2000$ is spent on radio ads and $1000 is spent on direct-mail is",
            sales_function(x2)*1000, "$"))
print(paste("Sales when 1000$ is spent on radio ads and $0 is spent on direct-mail is",
            sales_function(x3)*1000, "$"))
print(paste("Sales when 1000$ is spent on radio ads and $2000 is spent on direct-mail is",
            sales_function(x4)*1000, "$"))

```

Observation: When the same amount of money is allocated to direct-mail and radio advertising, the sales generated from radio advertising is much higher than the the case of direct-mail.

## Question b

Decision variables:\
$x \in \mathbb{R}^2$, $\mathbf{x}^\top = [x_1, x_2]$: amount of money spending on each advertising method

Objective function coefficients:\
$Q \in \mathbb{R}^{2 \times 2}$, $Q = \begin{bmatrix} -3 & -3 \\ -3 & -8 \end{bmatrix}$: quadratic term coefficient matrix\
$c \in \mathbb{R}^2$, $\mathbf{c}^\top = \begin{bmatrix} 16 & 34 \end{bmatrix}$: linear term coefficient vector

Constraint coefficients:\
$A \in \mathbb{R}^{1 \times 2}$, $A = \begin{bmatrix} 1 & 1 \end{bmatrix}$\
$b \in \mathbb{R}^1$, $b = [3]$

Objective function:\
Maximizing the sales generated from advertising
$$ \max f(\mathbf{x}) = \frac{1}{2} \mathbf{x}^\top Q \mathbf{x} + \mathbf{c}^\top \mathbf{x} $$

Constraints:\
The total spending on advertising must not exceed the budget
$$ Ax \leq b $$

The spending for each advertising method must be non-negative
$$ x \geq 0 $$

## Question c

Solving using quadratic function (the result of this function is not recognized for further tasks)

```{r}
# Import library
library(ROI)

# Define the quadratic term (Q) and linear term (c)
Q <- matrix(c(-3, -3, -3, -8), nrow = 2, byrow = TRUE)
C <- c(16, 34)

# Define the constraint matrix (A) and constraint values (b)
A <- matrix(c(1, 1), nrow = 1, byrow = TRUE)
b <- c(3)
dircon <- c("<=")

# Setup solver and solve the problem
qp <- OP(maximum = TRUE, 
         objective = Q_objective(Q = Q, L = C, names = c("x1","x2")),
         constraints = L_constraint(L = A, dir = dircon, rhs = b),
         types = c("C","C"))
qp

solution_qp <- ROI_solve(qp, solver = 'nloptr.cobyla', 
                         control = list(start = c(0,0)))

print(paste("Optimal decision variable is", solution_qp$solution))
print(paste("Optimial objective value is", solution_qp$objval))
```

Solving using nonlinear programming function (the result of this function is recognized for further tasks)

```{r}
# Objective function
sales_function

# Constraint function
A <- function(x) {
  return(x[1] + x[2]) 
}

# Constraint direction
condir <- c("<=")

# Constraint RHS
b <- 3

# Solve the problem

nlp <- OP(F_objective(sales_function, n = 2), 
          constraints = F_constraint(F = A, dir = condir, rhs = b), 
          maximum = TRUE)
nlp

solution_nlp <- ROI_solve(nlp, 
                          solver = "nloptr.cobyla", 
                          control = list(start = c(0,0)))

# Print result
print(paste("Optmial decision variable is", 
            solution_nlp$solution))
print(paste("Optimial objective value is", 
            solution_nlp$objval))

print(paste("Budget share for radio advertising is",
            solution_nlp$solution[1]/b*100, "%"))
print(paste("Budget share for direct-mail is",
            solution_nlp$solution[2]/b*100, "%"))
print(paste("The remaining budget is", 
            (1-solution_nlp$solution[1]/b-solution_nlp$solution[2]/b)*100,
            "%"))
print(paste("The expected generated sales due to the advertising campaign is",
            solution_nlp$objval))
```

The budget is not fully utilize in the optimal solution because in the sales generated function we have the negative coefficient with quadratic terms $-3x_1^2 - 8x_2^2$. Therefore, when we utilize all the budget, we will get a enormous negative value by $-3x_1^2 - 8x_2^2$ which the linear term $16x_1 + 34x_2$ cannot cover and the final result will be negative.\

# Problem 5

## Question a

```{r}
# Clear environment
rm(list=ls())

# Read the data
data <- read.csv("D:\\WU\\SCA1\\Exercise 2\\delhi_bus_network_hw2.csv")

# Print the result
print(paste("There are", length(unique(data$source)), "nodes")) 
print(paste("There are", length(data$weight), "edges"))
```

## Question b

```{r}
# Create edge_list from dataframe
edge_list <- as.matrix(data)

# Create graph
g <- graph_from_edgelist(el = edge_list[,1:2], directed = TRUE)
E(g)$weight <- edge_list[,3]

# Compute the shortest path when going from stop Sukhram.Nagar to Naroda.Terminus
path <- shortest_paths(g, 
                       from = "Sukhram.Nagar", 
                       to = "Naroda.Terminus", 
                       output = 'both')
print(path$vpath)

# Print number of bus change
print(paste("Number of bus changes:", length(path$vpath[[1]]) - 1))

# Compute the traveling time
time <- distances(g, 
                  v= "Sukhram.Nagar",
                  to = "Naroda.Terminus", 
                  mode = "out",
                  weights = E(g)$weight)

print(paste("The traveling time is:", time))
```

## Question c

```{r}
# Calculate all the paths
all_path <- distances(graph = g, mode = "out", weights = E(g)$weigth)

# Calculate maximum time
max_time <- max(all_path, na.rm = TRUE)
print(paste("Maximum time if travelling between any pair of bus stop is", 
            max_time))

# Figure out the max path
max_path <- which(all_path == max_time, arr.ind = TRUE)
from_node <- V(g)[max_path[1, 1]]$name
to_node <- V(g)[max_path[1, 2]]$name
print(paste("The longest shortest path is from", from_node, 
            "to", to_node))

print(paste("Number of bus changes:", 
            length(shortest_paths(g, 
                                  from = from_node, 
                                  to = to_node, output = 'both')$vpath[[1]]) - 1))

```









